---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ecofor

<!-- badges: start -->

<!-- badges: end -->

The goal of ecofor is to ...

## Installation

You can install the development version of ecofor from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("fahrihasby/ecofor")
```

or with:

``` r
#install.packages("devtools")
devtools::install_github("fahrihasby/ecofor")
```

## Example

This is a basic example which shows you how to calculate the importance value index of tree species at a sampling plot:

```{r example}
library(ecofor)
IVI(Papandayan)
## basic example code
```

You can also take advantage of the 'ggplot2' package to visualise the importance value index, for example:

```{r bar_plot_IVI}
library(ecofor)
df <- IVI(Papandayan)
library(ggplot2)
ggplot(data = df, aes(reorder(Species, -IVI),IVI)) +
  geom_bar(stat = "identity") +
  labs(x = "Species", Y = "Importance value index") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

or you can also display the component with this

```{r stacked_bar_plot_IVI}
library(ecofor)
library(data.table)
df <- melt(IVI(Papandayan)) # melt data
df <- df[df$variable != "IVI",] # filter out IVI
df$Species <- factor(df$Species, levels = unique(df$Species))#keep order of Species

library(ggplot2)
ggplot(data = df[df$variable != "IVI",], 
       aes(Species, value, fill = variable)) +
  geom_bar(position = "stack", stat = "identity") +
  labs(x = "Species", Y = "Importance value index") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
